\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Benjamin Wozak} % Your name
\address{126 14 Avenue SW, Calgary Alberta, Canada T2R-0L9} 
\address{+1 403 383 8294 \\ benwozak@gmail.com}
\sociallinks{
  \href{https://www.linkedin.com/in/ben-wozak/}{ \faLinkedin\ LinkedIn} \socialSep
  \href{https://github.com/benWozak/}{ \faGithub\ GitHub} \socialSep
  \href{https://benwozak.netlify.app/}{ \faGlobe\ Portfolio}
}
\begin{document}

\begin{rSection}{Profile}
  I am a highly motivated software developer with over five years of experience designing and developing user-interfaces 
  for B2B SaaS products as well as client-facing websites. I specialize in all things JavaScript to create elegant user 
  experiences for complex software solutions. I am seeking an intermediate/senior developer role to drive innovative 
  projects and mentor junior members.
\end{rSection}


\begin{rSection}{Experience}

    \begin{rSubsection}{Flipp Advertising Inc.}{\em Nov 2023 - July 2024}{Sr. Web Developer}{}
      \item Led cross-functional collaboration in agile environment practices, managing multiple projects to meet client specs, deadlines, and ongoing maintenance.
      \item Designed and built scalable infrastructure from the ground up for an industry-leading NextJS platform, supporting over 50,000 peak users each year.
      \item Optimized website performance and SEO, significantly improving load times and search rankings.
    \end{rSubsection}
    \begin{rSubsection}{Chata Technologies Inc.}{\em Sept 2019 - Nov 2023}{Team Lead/Frontend Software Engineer}{}
      \item Led two 4-person teams: one developing an internal ML model configuration web app, another creating AutoQL suite with chat interface, dashboard, and notification system.
      \item Developed 2 API portals and Microsoft Teams extension, serving hundreds of users across multiple SaaS platforms.
      \item Spearheaded company-wide TypeScript adoption and group code-reviews through dev guild leadership.
    \end{rSubsection}
    \begin{rSubsection}{KRD Consulting}{\em April 2019 - Nov 2019}{Jr. Web Developer}{}
      \item Modernized a database management system, integrating custom reporting and form creation tools.
      \item Created network visualization tool for enhancing non-profit collaboration.
      \item Managed and optimized custom DrupalCMS client site.
    \end{rSubsection}
    
\end{rSection}

\begin{rSection}{Technical Strengths}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Languages \ & TypeScript/JavaScript, HTML/CSS, Python, PHP  \\
    Frameworks & React, NextJS, express/node.js, SASS/tailwind, Vue.js, Laravel \\
    Tools & Github, BitBucket, Docker \\
    Databases & MySql, Sqlite, Postgres \\
    Cloud Technologies & AWS, Vercel, Netlify, Laravel Forge \\
    Industry & Requirements Analysis, Object-Oriented Programming (OOP), \\ 
     & Full-stack REST Development, Monolithic \& Microservice Architecture, \\
     & Developer Documentation \\
    \end{tabular}
    
\end{rSection}


% \begin{rSection}{Projects}
% {\bf GitHub Notifier}
% \\This project aims at providing real time information of events from GitHub and notify you accordingly. The project is in ready-to-deployment stage on a demo server as a cron-job. The notification engine  used for real time tracking is completely based on the python implementation assembled in an Android App with firebase cloud support.

% {\bf GitHub Notifier}
% \\This project aims at providing real time information of events from GitHub and notify you accordingly. The project is in ready-to-deployment stage on a demo server as a cron-job. The notification engine  used for real time tracking is completely based on the python implementation assembled in an Android App with firebase cloud support.

% \end{rSection}

\begin{rSection}{Education}

{\bf Southern Alberta Institute of Technology, Calgary AB} \hfill {\em Sept 2017 - May 2019} 
\\ Diploma, Information Technologies: Software Development.\hfill { Overall GPA: 3.5 }

\end{rSection}


\end{document}